---
title: "Map of SEANNET case studies"
author: "Timothée Flutre"
date: "17/06/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
out.dir = Sys.getenv("HOME")
if(Sys.info()["user"] == "marielcao"){
  out.dir = paste0(out.dir, "/Desktop")
}
stopifnot(dir.exists(out.dir))
```

This document is available under the following license: Creative Commons Attribution-ShareAlike 4.0 International ([CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/)).

More information about the Southeast Asia Neighborhoods Network (SEANNET) projet is available [here](http://www.ukna.asia/seannet).

Load packages:
```{r}
suppressPackageStartupMessages(library(rworldmap))
```

Retrieve the map of the world, and plot it, zooming in on the area of interest:
```{r}
map1 <- getMap(resolution = "low")
xlim = c(105, 138)
ylim = c(-9.2, 28)
plot(map1, xlim=xlim, ylim=ylim, asp=1)
```

Get country codes in the ISO 3 format ([source](http://www.nationsonline.org/oneworld/country_code_list.htm)):
```{r}
(country.codes = setNames(c("THA", "MMR", "VNM", "PHL", "IDN"),
                         c("Thailand", "Myanmar", "Viet Nam", "Philippines", "Indonesia")))
```

Color these countries on the map:
```{r}
countries <- data.frame(country = country.codes,
                        merge = rep(1, length(country.codes)))
newmap <- joinCountryData2Map(countries,
                              joinCode = "ISO3",
                              nameJoinColumn = "country")
mapCountryData(mapToPlot = newmap,
               xlim=xlim, ylim=ylim,
               nameColumnToPlot = "merge",
               catMethod = "categorical",
               colourPalette = rep("grey", nrow(countries)),
               borderCol = "black",
               mapTitle = "SEANNET case studies",
               addLegend = FALSE)
```

Get city GPS coordinates ([source](https://itouchmap.com/latlong.html)):
```{r}
(cities = data.frame(city = c("Chiang Mai", "Bangkok", "Mawlamyine", "Ho Chi Minh City", "Manila", "Surabaya"),
                     neihborhood = c("Wu alai", "Wat Kae Nang Leong", "Aukkyin Ward", "Phu Nhuan", "Escolta Santa Cruz", "Kampung Peneleh"),
                     country = c("Thailand", "Thailand", "Myanmar", "Viet Nam", "Philippines", "Indonesia"),
                     lat = c(18.777932, 13.759305, 16.454317, 10.793254, 14.597931, -7.253189),
                     lon = c(98.983931, 100.512226, 97.643961, 106.685185, 120.978653, 112.740538)))
coordinates(cities) = c("lon", "lat")
```

Add cities to the map:
```{r}
plot(cities, xlim=xlim, ylim=ylim, type="n", col = "red", pch = 20)
mapCountryData(mapToPlot = newmap,
               xlim=xlim, ylim=ylim,
               nameColumnToPlot = "merge",
               catMethod = "categorical",
               colourPalette = rep("grey", nrow(countries)),
               borderCol = "black",
               mapTitle = "SEANNET case studies",
               addLegend = FALSE, add = T)
plot(cities, col="red", add = TRUE, pch = 20)
```

Save in the PNG format:
```{r}
out.dir
png(filename = paste0(out.dir, "/map_SEANNET_case_studies.png"),
    title = "SEANNET case studies",
    width = 15, height = 10, units = "cm", res = 500, pointsize = 12)
par(mar = c(0, 0, 0, 0) + 0.2)
plot(cities, xlim=xlim, ylim=ylim, type="n", col = "red", pch = 20)
mapCountryData(mapToPlot = newmap,
               xlim=xlim, ylim=ylim,
               nameColumnToPlot = "merge",
               catMethod = "categorical",
               colourPalette = rep("grey", nrow(countries)),
               borderCol = "black",
               mapTitle = "",
               addLegend = FALSE, add = T)
plot(cities, col="red", add = T, pch = 20)
dev.off()
```

This PNG file can be included in any media, as long as the following information is present ([details](https://wiki.creativecommons.org/wiki/Best_practices_for_attribution)):

* author: `Timothée Flutre`;

* source: `MapsMisc at github.com` or `https://github.com/timflutre-perso/MapsMisc`;

* license: `CC BY-SA 4.0`.

It can be a single line below the image:

`Timothée Flutre (2017), MapsMisc at github.com, CC BY-SA 4.0`;

or a sentence, such as:

`Map of the SEANNET case studies by Timothée Flutre licensed under the Creative Commons Attribution-ShareAlike 4.0 license`.

For something even shorter, the bare minimum would be:

`T. Flutre (2017) CC BY-SA`.

Enjoy!

TF
